\documentclass[10pt, letterpaper]{article}

\usepackage[
    ignoreheadfoot,
    top=1cm,
    bottom=1.5cm,
    left=2cm,
    right=2cm,
    footskip=1cm,
]{geometry}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage[
    pdftitle={Marwan Maher Mostafa — CV},
    pdfauthor={Marwan Maher Mostafa},
    pdfcreator={LaTeX},
    colorlinks=true,
    urlcolor=MidnightBlue
]{hyperref}
\usepackage{eso-pic}
\usepackage{bookmark}
\usepackage{paracol}
\usepackage{charter}
\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

\pagestyle{empty}
\raggedright
\setlength{\parindent}{0pt}
\setlength{\columnsep}{0.15cm}
\pagenumbering{gobble}

\titleformat{\section}{\large\bfseries}{}{0pt}{}[\titlerule]
\titlespacing{\section}{0pt}{0.3cm}{0.2cm}

\renewcommand\labelitemi{\small$\bullet$}
\newenvironment{highlights}{
    \begin{itemize}[topsep=0.10cm, parsep=0.07cm, partopsep=0pt, itemsep=0pt, leftmargin=10pt]
}{
    \end{itemize}
}

\newenvironment{header}{
    \centering\linespread{1.5}
}{
    \par\kern\topsep
}

\begin{document}

% ═══════════════════════════════════════════════════
%  HEADER
% ═══════════════════════════════════════════════════
\begin{header}
    {\LARGE \textbf{Marwan Maher Mostafa}} \\[2pt]
    {\small Developer \& Project Manager} \\[4pt]
    \href{mailto:Marwanmaher635@gmail.com}{\faEnvelope\ Marwanmaher635@gmail.com} \textbar{}
    \href{tel:+201025027019}{\faPhone\ +20 102 502 7019} \textbar{}
    \faMapMarker*\ Assiut, Egypt \\[3pt]
    \href{https://www.linkedin.com/in/marwan-maher-b11628227}{\faLinkedin\ LinkedIn} \textbar{}
    \href{https://github.com/MarwanMaher0}{\faGithub\ GitHub} \textbar{}
    \href{https://marwanmaher0.github.io}{\faGlobe\ Portfolio}
\end{header}

\vspace{0.2cm}

% ═══════════════════════════════════════════════════
%  SUMMARY
% ═══════════════════════════════════════════════════
\section{Professional Summary}
Full-stack developer turned project manager with 3+ years of experience shipping \textbf{15 production applications} across enterprise SaaS, healthcare, AI/AR, and e-commerce. Promoted twice at SIPRC — from Senior Front-End to Full Stack to \textbf{Project Manager leading a team of 6} across 4 enterprise IP products serving the Saudi government market. Core stack: Vue 3/Nuxt, Next.js/React, TypeScript, Three.js, TensorFlow.js, with full-stack reach into Django and Laravel.

% ═══════════════════════════════════════════════════
%  EXPERIENCE
% ═══════════════════════════════════════════════════
\section{Experience}

\textbf{Project Manager $\vert$ Senior Front-End $\rightarrow$ Full Stack Developer} \hfill \textbf{2025 – Present} \\
\textit{Saudi Intellectual Property Rights Company (SIPRC) — Riyadh, KSA} \\
\begin{highlights}
    \item Promoted twice in under a year to \textbf{Project Manager leading a team of 6 developers} across 4 enterprise products — IPORA, Cepro Dashboard, Cepro.ai, and SIPRC Website.
    \item Built \textbf{IPORA} (307 components, 44 routes) — flagship IP portfolio platform covering Trademarks, Patents, Copyrights, and Industrial Designs with granular RBAC, now used daily by SIPRC's operations teams. \href{https://dbp.siprc.sa}{[\,dbp.siprc.sa\,]}
    \item Developed \textbf{Cepro Dashboard} (211 components, 4-tier RBAC) — brand protection platform monitoring IP infringement across web, social media, apps, and dark web with SLA-tracked takedowns. \href{https://dbp.cepro.ai}{[\,dbp.cepro.ai\,]}
    \item Led \textbf{Cepro.ai} rebuild with Next.js 15 + React 19 — 17 pages, in-browser Arabic OCR via Tesseract.js, delivered 2 weeks ahead of deadline. \href{https://www.cepro.ai/en}{[\,cepro.ai\,]}
    \item Established QA practice from scratch: Selenium automation suite with \textbf{530+ test cases across 170+ features}, reducing manual regression by \textbf{40\%}.
    \item Authored 59-page VitePress developer documentation, cutting new-developer onboarding time in half.
\end{highlights}

\textbf{Front-End Developer} \hfill \textbf{2023 – 2024} \\
\textit{Digitee — AI-Powered Fashion Technology (Remote)} \\
\begin{highlights}
    \item Sole front-end developer who built \textbf{6 production applications} for an AI fashion startup — from zero to launch across consumer, e-commerce, B2B, and operations.
    \item Developed \textbf{AR virtual try-on} (TensorFlow.js + MediaPipe Pose) and a \textbf{Three.js 3D Showroom}, enabling customers to visualize products before purchase.
    \item Shipped \textbf{multi-region e-commerce} serving 5 countries (US, Egypt, Qatar, UAE, Saudi Arabia) with geo-aware routing, dual payment gateways (PayPal + Kashier), and 5-language support.
    \item Created \textbf{Mintora} print-on-demand platform (307 components) with FullCalendar scheduling and public QR-code order tracking for factory floor access.
    \item Built B2B enterprise dashboard (212 components) with AI image generation, token usage analytics, and \textbf{16-language i18n} including full RTL.
\end{highlights}

\textbf{Front-End Developer} \hfill \textbf{2022 – 2023 \normalfont{(6 months, concurrent with freelance)}} \\
\textit{IDAAM — Brain Health Technology (USA, Remote)} \\
\begin{highlights}
    \item Built front-end for \textbf{Keme}, a full-scale US clinic management platform — 552 Vue files powering 65 modules (Patients, Providers, Appointments, Telehealth, Billing, Lab, AI Notes). \href{https://dev.id3m.dev}{[\,dev.id3m.dev\,]}
    \item Integrated telehealth video (Jitsi), VoIP (RingCentral), payments (Stripe), and real-time updates (Pusher WebSockets) into a unified patient experience.
    \item Collaborated with a Laravel backend team across 1,509 API routes and 402 database migrations; implemented RBAC, Elasticsearch search, and Google 2FA.
\end{highlights}

\textbf{Front-End Developer (Freelance)} \hfill \textbf{2022 – 2023} \\
\begin{highlights}
    \item Delivered 4 client projects independently: \textbf{Climate Risk Assessment Tool} (PhD research, Leaflet maps + PDF export), \textbf{Lusion 3D} (Three.js WebGL recreation with cloth physics), fitness \textbf{e-commerce} (Django REST backend), and a \textbf{User Management Dashboard} (TypeScript, Cypress E2E, EN/AR RTL).
\end{highlights}

% ═══════════════════════════════════════════════════
%  TECHNICAL SKILLS
% ═══════════════════════════════════════════════════
\section{Technical Skills}

\textbf{Front-End:} Vue 3, Nuxt 3, React, Next.js, TypeScript, JavaScript (ES6+), Tailwind CSS, Vuetify, SCSS, Three.js, GSAP \\[3pt]
\textbf{Back-End \& Data:} Django REST, Laravel, PostgreSQL, MySQL, Redis, Elasticsearch, Docker, AWS S3 \\[3pt]
\textbf{AI / AR / Web3:} TensorFlow.js (BodyPix, MediaPipe), Three.js/WebGL, MetaMask SDK, ethers.js, WalletConnect \\[3pt]
\textbf{Testing \& QA:} Playwright, Cypress, Selenium (530+ cases), Vitest, CI/CD pipelines \\[3pt]
\textbf{State \& i18n:} Pinia, Redux Toolkit, vue-i18n, next-intl, RTL/LTR, WCAG 2.1, up to 16 locales \\[3pt]
\textbf{Leadership:} Agile/Scrum, cross-functional team management, code review, VitePress documentation, Mixpanel analytics

% ═══════════════════════════════════════════════════
%  LANGUAGES
% ═══════════════════════════════════════════════════
\section{Languages}
\textbf{Arabic} — Native \textbar{} \textbf{English} — Professional working proficiency

% ═══════════════════════════════════════════════════
%  EDUCATION
% ═══════════════════════════════════════════════════
\section{Education}
\textbf{Bachelor of Computer Science}, Assiut University — Assiut, Egypt \hfill \textbf{2019 – 2023} \\
Software engineering, data structures \& algorithms, databases, and system design.

\end{document}
